---
title: "Creating the ``r params$package_name`` R package"
author: "Jacob Bien"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
knit: litr::render
output: litr::litr_gitbook
params:
  package_name: "example" # <-- change this to your package name
  package_parent_dir: "." # <-- relative to this file's location
documentclass: book
---

# Introduction

A nicely rendered version of this bookdown is available [here](https://jacobbien.github.io/example/create/).

The pkgdown website for this package is available [here](https://jacobbien.github.io/example/).



# Package setup

Every R package needs a DESCRIPTION file, so we start by specifying this information:

```{r package-setup, message=FALSE, results='hide'}
usethis::create_package(
  path = ".",
  fields = list(
    Package = params$package_name,
    Version = "0.0.0.9000",
    Title = "A Package Defined in a Bookdown",
    Description = "This package uses litr to define an R package through writing a bookdown.",
    `Authors@R` = person(
      given = "First",
      family = "Last",
      email = "you@gmail.com",
      role = c("aut", "cre")
      )
  )
)
usethis::use_mit_license(copyright_holder = "F. Last")
```

Although it's not required, it can be nice to add some package-level documentation.  This is what will show up when someone types `package?<your-package-name>` in the console.

```{package_doc}
#' A Package Defined in a Bookdown
#'
#' This package uses `litr` to define an R package through writing a `bookdown`.
#' 
#' @docType package
```

# The basics of saying hello

Let's define a function for our R package:

```{r}
#' Say hello to someone
#' 
#' @param name Name of a person
#' @param exclamation Whether to include an exclamation mark
#' @export 
say_hello <- function(name, exclamation = TRUE) {
  paste0("Hello ", name, ifelse(exclamation, "!", "."))
}
```

Code chunks whose first line starts with `#'` are added to the package.

We can try running it.

```{r}
say_hello("Jacob")
```

That code chunk does not start with `#'`, so it is not added to the package.

Let's write some tests to make sure the function behaves as desired:

```{r}
testthat::test_that("say_hello works", {
  testthat::expect_equal(say_hello("Jacob"), "Hello Jacob!")
  testthat::expect_equal(say_hello("Jacob", exclamation = FALSE), "Hello Jacob.")
})
```

Code chunks that have one or more lines starting with `test_that(` (or `testthat::test_that(`) are added to the package as tests.

# Generalization to other greetings

We can now get fancier and define more functions across as many .Rmd files as we like.  Hyperlinks work across different .Rmd files.  For example, you can click on `say_hello()` and it will bring you to the definition in the previous chapter.

# Conclusion {#conclude}

When you are done defining the package, it remains to convert the Roxygen to documentation.

```{r}
litr::document() # <-- use instead of devtools::document()
```

You can also add some extra things to your package here if you like, such as a README, some vignettes, a [pkgdown](https://pkgdown.r-lib.org/) site, etc.  See [here](https://github.com/jacobbien/litr-project/tree/main/examples/make-an-r-package-with-extras) for an example of how to do this with `litr`.


## Add README

```{r}
litr::add_readme("../source-files/README.Rmd")
```

## Add pkgdown


```{r}
litr::add_pkgdown("../source-files/_pkgdown.yml")
```
